Project-I by Group CITYNAME

### 2015-10-31 report/paper.tex
Added Logistic regression section"

>>>>

\section{Logistic Regression}
\subsection{Data Description}
Our second data set consisted of a train set, with an input and an output binary
variable respectively $\mathbf{X}$ and $\mathbf{y}$, composed of $N=1500$ data
samples, and a test set with only $\mathbf{X}$ variable observed and $N=1500$
data samples. $\mathbf{X}$ spans over $D=34$ features, among which 5 of them are
categorical, with number of categories ranging from 1 to 5.

The categorical variables were encoded using dummy encoding, what led to a total
feature number of 47. As the rank of our dataset is below 47 (it is 42), we use penalized logistic regression to cope for the rank deficiency.

Our goal is to produce binary classification predictions for test examples and approximate the test error.

\subsection{Data visualization and cleaning}
Firstly, the data input $\mathbf{X}$ train and $\mathbf{Y}$ train variables was visualized. The figures are showed in \ref{fig:yTrainClass} and \ref{fig:boxplotXClass}. After plotting this figures, all -1 values were changed on 0 in $\mathbf{Y}$ train and $\mathbf{X}$ train variables were normalized (normalizing the output variable allow us to obtain convergence faster with gradient decent and Newton's method). We tried gradient decent and Newton`s method for Logistic regression and Penalized Logistic Regression  and chose Newton`s method as the execution time was nearly the same, but Newton`s method was converged better than gradient descent method(as we needed to changing alpha parameter too) and with less iterations.

Plotting histogram graphs for each variable in $\mathbf{X}$ train, showed that features have different distributions and mostly do not follow to normal Gaussian distribution.

\begin{figure}[!t]
\center
\subfigure[Histogram of $\mathbf{Y}$ train.]{\includegraphics[width=2.0in]{figures/HistY.png} \label{fig:yTrainClass}}
\subfigure[Boxplot of $\mathbf{X}$ train.]{\includegraphics[width=3.3in]{figures/boxplotX.png} \label{fig:boxplotXClass}}
\hfill
\caption{}
\end{figure}

\subsection{Penalized Logistic regression}
We applied logistic regression and penalized logistic regression method for dataset. As we have many features, we expected that Penalized Logistic regression will improve test error result for kFold cross-validation with $k=4$ by penalizing some features. But the test 1-0 loss error for both methods was nearly the same and equals $0.183\pm0.001$.The summarized result with lambda in range between $10^{-4}$ to $10^3$  with 100 points presented in the Figure \ref{fig:pen}.

\subsection{Feature transformation}
Several features transformations were performed. Features deleting or using only classified features did not improve prediction result. Then we applied polynomial function transformation for each feature. We tried the same approach as with linear regression, we found features with two modes histogram distribution (the hypothesis is that features follow 0 and 1 output result) and use only them with polynomial feature transformation, but it did not improve the error result too.

We compared penalized logistic regression without features engineering results with polynomial transformation. Method with transformation showed better result and gave the 1-0 loss test error result  $0.167\pm0.001$. The lambda parameter in case without feature transformation was chosen equal 0.001 and with feature transformation was chosen equal to 0.3 according to result of a k-fold cross validation procedure with $k=4$ and lambda in range between $10^{-3}$ to $10^4$  with 100 points. The result described here are summarized in the Figure \ref{fig:pen} and \ref{fig:poly_pen}.

\begin{figure}[!t]
\center
\subfigure[Penalized logistic regression on kFold with $k=4$.]{\includegraphics[width=2.69in]{figures/pen_lambda.png} \label{fig:pen}}
\subfigure[Penalized logistic regression on kFold with $k=4$ and feature feature transformation.]{\includegraphics[width=2.69in]{figures/pen_lambda_poly.png} \label{fig:poly_pen}}
\hfill
\caption{}
\end{figure}

\section{Summary}

\section{Acknowledgments}
We would like to thank Emtiyaz Khan and all teacher`s advisers for making the datasets for this project and answering our question during exercise sessions.

The regression part was done by Corentin Tallec, as well as section Linear regression of report. The classification part was done by Roman Shirochenko, as well as the Classification part of the report.
